### 2023-08-01 inst/reproduce_results/results.Rmd
Fixed subsetting bug
Caused problems in windows

tiemeans = c(450,3000,8500)
tiesds = c(100,500,200)
res3 = tiepointsimmer(res,synchronization = list(locations=tiedepths,
                                                locations_unit="depth",
                                                method="normal",
                                                params=list(mean=tiemeans,
                                                            sd=tiesds))
               )
res3 = bremla_synchronized_simulation(res3,control.sim=list(synchronized=TRUE))
ggd = data.frame(depth=res3$data$depth,
                 mean = res3$simulation$summary_sync$mean-orichron,
                 lower = res3$simulation$summary_sync$lower-orichron,
                 upper = res3$simulation$summary_sync$upper-orichron)
ggd_2 = data.frame(depth=res3$data$depth,
                 mean = res3$simulation$summary_sync$mean,
                 lower = res3$simulation$summary_sync$lower,
                 upper = res3$simulation$summary_sync$upper)

@@

ylim = range(res$simulation$summary$lower,res$simulation$summary$upper,
             res3$simulation$summary_sync$lower,res3$simulation$summary_sync$upper)
ggpunc2 = ggpunc2 + ylim(ylim) + ggtitle("(a) Unsynchronous chronologies")+ylab("Ensemble age")
ggpfix2 = ggpfix2 + ylim(ylim)+ ggtitle("(b) Synchronous chronologies: fixed tie-points")+ylab("Ensemble age")
ggprand2 = ggprand2 + ylim(ylim)+ ggtitle("(c) Synchronous chronologies: uncertain tie-points")+ylab("Ensemble age")
ggplotlist1 = c(); ggplotlist1[[1]] = ggpunc2; ggplotlist1[[2]] = ggpfix2; ggplotlist1[[3]] = ggprand2
ggplotarrange = ggarrange(plotlist=ggplotlist1,nrow=3,ncol=1)
plot(ggplotarrange)
ggsave("illustrative-all-3000x3000.eps",device=cairo_ps,width=3000,height=3000,units="px")

@@

  dsims = colDiffs(rbind(matrix(rep(res$initial$age,ncol(res$simulation$age)),nrow=1), res$simulation$age))
  dmeans = rowMeans(dsims)
  dsd = rowSds(dsims)
ggd = data.frame(y = res$data$dy,depth=res$data$depth,
                   mean=dmeans,
                   lower = dmeans-1.96*dsd,
                   upper = dmeans+1.96*dsd)
  ggp = ggplot(data=ggd,aes(x=depth)) + theme_bw()+ #xlim(rev(range(results$data$depth)))+
    geom_line(aes(y=y),col="gray")+
    geom_line(aes(y=mean),col="blue",size=0.8)+
    geom_ribbon(aes(ymin=lower,ymax=upper),color="red",alpha=0,size=0.8)+
    xlab("Depth (m)")+ylab("Layers per 5cm")+ggtitle("(a) Fitted layer increment model")

@@

 reference=res$original.chron$age[1+1:n]
 reftie = reference[res$tie_points$locations_indexes]
ggdtie = data.frame(mean=synchronization$params$mean-reftie,
                    upper=synchronization$params$mean+1.96*synchronization$params$sd-reftie,
                    lower=synchronization$params$mean-1.96*synchronization$params$sd-reftie,
                    locations = res$data$depth[synchronization$locations])
ggp2 = ggplot(data=ggd2,aes(x=depth)) + theme_bw()+
  geom_ribbon(aes(ymin=lower,ymax=upper),color="red",fill="red",alpha=0.3)+
  geom_line(aes(y=mean),color="blue") +
  geom_linerange(data=ggdtie,aes(x=locations,ymin=lower,ymax=upper),color="magenta")+
  xlab("Depth (m)") + ylab("Deviation from simulated reference (years)")+
  ggtitle("(b) Simulated chronologies")

@@

library(gridExtra)
# ggsave("fitdiffsim-5500x4000.eps", device=cairo_ps,width=5500,height=4000,units="px",dpi=500,limitsize=FALSE,arrangeGrob(ggp,ggp2))
dig=3
str = ""
str = paste0(str, " $",namevals[1],"$ & ",truevals[1]," & ", format(res$fitting$inla$hyperparameters$results$sigma_epsilon$mean,digits=dig,scientific=FALSE)," & (",format(res$fitting$inla$hyperparameters$results$sigma_epsilon$quant0.025,digits=dig,scientific=FALSE), ", ",format(res$fitting$inla$hyperparameters$results$sigma_epsilon$quant0.975,difits=dig,scientific=FALSE),") \\\\ \n")

>>>>

tiemeans = c(450,3000,8500)
tiesds = c(100,500,200)
res3 = tiepointsimmer(res,synchronization = list(locations=tiedepths,
                                                locations_unit="depth",
                                                method="normal",
                                                params=list(mean=tiemeans,
                                                            sd=tiesds))
               )
res3 = bremla_synchronized_simulation(res3,control.sim=list(synchronized=TRUE))

ggd = data.frame(depth=res3$data$depth,
                 mean = res3$simulation$summary_sync$mean-orichron,
                 lower = res3$simulation$summary_sync$lower-orichron,
                 upper = res3$simulation$summary_sync$upper-orichron)
ggd_2 = data.frame(depth=res3$data$depth,
                 mean = res3$simulation$summary_sync$mean,
                 lower = res3$simulation$summary_sync$lower,
                 upper = res3$simulation$summary_sync$upper)

@@

ylim = range(res$simulation$summary$lower,res$simulation$summary$upper,
             res3$simulation$summary_sync$lower,res3$simulation$summary_sync$upper)
ggpunc2 = ggpunc2 + ylim(ylim) + ggtitle("(a) Unsynchronous chronologies")+ylab("Ensemble age")
ggpfix2 = ggpfix2 + ylim(ylim)+ ggtitle("(b) Synchronous chronologies: fixed tie-points")+ylab("Ensemble age")
ggprand2 = ggprand2 + ylim(ylim)+ ggtitle("(c) Synchronous chronologies: uncertain tie-points")+ylab("Ensemble age")
ggplotlist1 = c(); ggplotlist1[[1]] = ggpunc2; ggplotlist1[[2]] = ggpfix2; ggplotlist1[[3]] = ggprand2
ggplotarrange = ggarrange(plotlist=ggplotlist1,nrow=3,ncol=1)
plot(ggplotarrange)

#ggsave("illustrative-all-3000x3000.eps",device=cairo_ps,width=3000,height=3000,units="px")
ggsave("illustrative-all-3000x3400.eps",device=cairo_ps,width=3000,height=3400,units="px",dpi=500,limitsize=FALSE)

#ggsave("illustrative-all-3000x4000.eps", device=cairo_ps,width=3000,height=4000,units="px",dpi=500,limitsize=FALSE,arrangeGrob(ggp,ggp2))

@@

  dsims = colDiffs(rbind(matrix(rep(res$initial$age,ncol(res$simulation$age)),nrow=1), res$simulation$age))
  dmeans = rowMeans(dsims)
  dsd = rowSds(dsims)
ggd = data.frame(y = res$data$dy,depth=res$data$depth,
                   mean=dmeans,
                   lower = dmeans-1.96*dsd,
                   upper = dmeans+1.96*dsd)
  ggp = ggplot(data=ggd,aes(x=depth)) + theme_bw()+ #xlim(rev(range(results$data$depth)))+
    geom_line(aes(y=y),col="gray")+
    geom_line(aes(y=mean),col="blue",size=0.8)+
    geom_ribbon(aes(ymin=lower,ymax=upper),color="red",alpha=0,size=0.8)+
    xlab("Depth (m)")+ylab("Layers per 1m")+ggtitle("(a) Fitted layer increment model")

@@

 reference=res$original.chron$age[1+1:n]
 reftie = reference[res$tie_points$locations_indexes]
ggdtie = data.frame(mean=synchronization$params$mean-reftie,
                    upper=synchronization$params$mean+1.96*synchronization$params$sd-reftie,
                    lower=synchronization$params$mean-1.96*synchronization$params$sd-reftie,
                    locations = res$data$depth[synchronization$locations])
ggp2 = ggplot(data=ggd2,aes(x=depth)) + theme_bw()+
  geom_ribbon(aes(ymin=lower,ymax=upper),color="red",fill="red",alpha=0.3)+
  geom_line(aes(y=mean),color="blue") +
  geom_linerange(data=ggdtie,aes(x=locations,ymin=lower,ymax=upper),color="magenta")+
  xlab("Depth (m)") + ylab("Age deviation (years)")+
  ggtitle("(b) Simulated chronologies")

@@

library(gridExtra)

# ggsave("fitdiffsim-5500x4000.eps", device=cairo_ps,width=5500,height=4000,units="px",dpi=500,limitsize=FALSE,arrangeGrob(ggp,ggp2))

ggsave("fitdiffsim-3000x2200.eps", device=cairo_ps,width=3000,height=2200,units="px",dpi=500,limitsize=FALSE,arrangeGrob(ggp,ggp2))

dig=3
str = ""
str = paste0(str, " $",namevals[1],"$ & ",truevals[1]," & ", format(res$fitting$inla$hyperparameters$results$sigma_epsilon$mean,digits=dig,scientific=FALSE)," & (",format(res$fitting$inla$hyperparameters$results$sigma_epsilon$quant0.025,digits=dig,scientific=FALSE), ", ",format(res$fitting$inla$hyperparameters$results$sigma_epsilon$quant0.975,difits=dig,scientific=FALSE),") \\\\ \n")
